preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution

### 2021-06-04 BMC_Genome_Biology_submission/grubert_manuscript_figures_tables/manuscript/manuscript_v1.Rmd
WIP

In contrast to low-resolution Hi-C data, functional/regulatory genome annotations (histone modifications, DNAse I hypersensitive sites, DNA methylation, and transcription factor binding sites (TFBSs)) assembled by the ENCODE [@ENCODE-Project-Consortium:2012aa] and other consortia have been profiled at relatively high resolution (10-300bp) [@Dozmorov:2017aa]. The one-dimensional genome annotation data has been used to predict functional chromatin contacts (e.g., HiC-Reg [@Zhang:2019aa]), boundaries of chromatin domains (e.g., Lollipop [@Kai:2018aa], 3DEpiLoop [@Al-Bkhetan:2018aa]), with 48 methods recently reviewed by Tao et al. [@Tao:2021uc]. The association of domain boundaries with CTCF and other genomic annotations [@dixon2012topological; @rao20143d; @Tang:2015aa; @Phillips:2009aa; @phillips2013architectural] holds promise that these high-resolution marks may inform the more precise location of domain boundaries.

@@

>>>>

In contrast to low-resolution Hi-C data, functional/regulatory genome annotations (histone modifications, DNAse I hypersensitive sites, DNA methylation, and transcription factor binding sites (TFBSs)) assembled by the ENCODE [@ENCODE-Project-Consortium:2012aa] and other consortia have been profiled at relatively high resolution (10-300bp) [@Dozmorov:2017aa]. The one-dimensional sequence- and genome annotation data has been used to predict functional chromatin contacts (e.g., HubPredictor [@huang2015predicting], HiC-Reg [@Zhang:2019aa]), boundaries of chromatin domains (e.g., Lollipop [@Kai:2018aa], 3DEpiLoop [@Al-Bkhetan:2018aa]), with 48 methods recently reviewed by Tao et al. [@Tao:2021uc]. The association of domain boundaries with CTCF and other genomic annotations [@dixon2012topological; @rao20143d; @Tang:2015aa; @Phillips:2009aa; @phillips2013architectural] holds promise that these high-resolution marks may inform the more precise location of domain boundaries.

@@

HubPredictor used histone marks and transcription factors [@huang2015predicting].

pTADs uses chromatin states, histones, TFBSs. Sequence properties - DNA shape (minor groove width, propeller twist, Roll, helix twist, calculated by DNAshape program, further transformed into seven statistical values like mean, RMSE, median, min/max, SD, population deviation), DNA properties (di-/trinucleotides etc. 139 properties total), TFBS motif occurrences (1442 PWMs), conservation score (PhastCons 46-way).
